Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
improve stacking section

\section{Stacking methodology}
\label{sec:stacking}
% Speak about why averaging
%In order to improve performance, we stacked the partial correlation matrix

Our first guess was that introduce an ensemble method would improve performance
[cite papers which praise ensemble methods]. Among all parameters of our method,
we choose to average over two parameters, i.e. over multiple combinations of the
hard-threshold value $f_3$ and the pattern of the low-pass filter $c_l$. In order to
free ourself from the choice of a probability distribution for the $(f_3,c_l)$ combinations,
we choose a uniform distribution for the threshold distribution (in a given interval of
values) within each filtering process and perform a weighted average for the low-pass
filter pattern. Formally, the stacked predicted adjacency matrix $y_{stacking}$ can be formulated by

\begin{align}
y_{stacking} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
\end{align}
where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the filtering and inference methodologies (as described
in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value $f_3$ for the
hard-threshold among a set of thresholds $T_k$ of size $|T_k|$ and the $k^{th}$ low-pass filter pattern associated
to a weight $w_k$ whose values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.

>>>>

\section{Stacking methodology}
\label{sec:stacking}

% Speak about why averaging
The quality of the signal filtering and network inference is dependent upon
good hyper-parameter selection, which are themselves dependent on the properties
of the targeted network and measurement conditions, e.g. signal to noise ratio.
Ensemble methods are known to improve robustness with respect to parameter
selection [todo cite] and improve performance [todo cite].
A weighted average $y_{stack}$ of partial correlation matrices was made
by varying uniformly the hard-threshold value (parameter $f_3$) and the design
of the low-pass filter (coefficients $c_l$). The stacked connectivity score
matrix $y_{stacking}$ is given by
\begin{align}
y_{stack} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
\end{align}
where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the
filtering and inference methodologies (as described
in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value
$f_3$ for the hard-threshold among a set of thresholds $T_k$ of size $|T_k|$
and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ whose
values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
